Determining sequence-dependent DNA oligonucleotide hybridization and dehybridization mechanisms using coarse-grained molecular simulation, Markov state models, and infrared spectroscopy

### 2021-05-17 manuscript.tex
Brennan edits

The sample was placed between two 1 mm thick CaF2 windows separated by a 50 $\mu$m Teflon spacer enclosed in a home-built brass jacket. The initial temperature of the sample was set using a recirculating chiller connected to the brass sample jacket. The T-jump temperature change ($\Delta$T) was set to 15 $^\circ$C for all measurements and monitored using the change in transmission of the \ce{D2O} bend-libration combination band measured in the LO beam. The temperature change was quantified by comparing the change in transmission of the LO beam with a FTIR temperature series of \ce{D2O}.

@@

\section{\label{sec:Results}Results}

@@

We present in Fig.~\ref{fig:T-jump_stretching} our T-jump IR t-HDVE difference spectra and corresponding normalized time traces at 1600 cm$^{-1}$ and 1660 cm$^{-1}$. The signal at 1600 cm$^{-1}$ corresponds to changes in A and T ring vibrations while the signal at 1660 cm$^{-1}$ contains contributions from G and T carbonyl vibrations. Each time trace was fitted to the sum of a stretched exponential and two exponentials $S(t) = A\exp{(-(t/\tau^{\mathrm{fast}})^{\beta})} + B\exp{(-t/\tau_{\mathrm{slow}})}+C\exp{(-t/\tau_{\mathrm{cool}})}$. The stretched exponential describes the relaxation process from 5 ns to 1 $\mu$s, and the two exponentials describe the signal increase from 1-320 $\mu$s and signal decay from re-hybridization induced by thermal relaxation back to the initial temperature. The fitting parameters $A$, $B$, and $C$ correspond to the relative amplitudes of the three kinetic responses and the stretch factor $\beta$ to the heterogeneity of fraying dynamics at the fast timescale. A testable prediction of our hypothesis is that the long-lived out-of-register shifted states in AT-all should result in a significantly smaller value for the fitted $\beta$ parameter relative to those for GC-end, GC-core, and GC-mix. This hypothesis was supported by the experimental time series at both 1600 cm$^{-1}$, where $\beta_\mathrm{AT-all}$ = 0.3 compared to $\beta_\mathrm{GC-end}$ = 0.6, $\beta_\mathrm{GC-core}$ = 0.7, and $\beta_\mathrm{GC-mix}$ = 0.6, and 1660 cm$^{-1}$, where $\beta_\mathrm{AT-all}$ = 0.4 compared to $\beta_\mathrm{GC-end}$ = 0.7, $\beta_\mathrm{GC-core}$ = 0.6, and $\beta_\mathrm{GC-mix}$ = 0.6. This result supports our hypothesis and validates a testable dynamical prediction of our sequence-dependent MSMs.

@@

>>>>

The sample was placed between two 1 mm thick CaF2 windows separated by a 50 $\mu$m Teflon spacer enclosed in a home-built brass jacket. The initial temperature of the sample was set using a recirculating chiller connected to the brass sample jacket. The T-jump temperature change ($\Delta$T) was set to 14-16 $^\circ$C for all measurements and monitored using the change in transmission of the \ce{D2O} bend-libration combination band measured in the LO beam. The temperature change was quantified by comparing the change in transmission of the LO beam with a FTIR temperature series of \ce{D2O}.

@@

\section{\label{sec:Results}Results and Discussion}

@@

We present in Fig.~\ref{fig:T-jump_stretching} our T-jump IR t-HDVE difference spectra and corresponding normalized time traces at 1600 cm$^{-1}$ and 1660 cm$^{-1}$. The signal at 1600 cm$^{-1}$ corresponds to changes in A and T ring vibrations while the signal at 1660 cm$^{-1}$ contains contributions from G and T carbonyl vibrations. Each time trace was fitted to the sum of a stretched exponential and two exponentials $S(t) = A\exp{(-(t/\tau_{\mathrm{fast}})^{\beta})} + B\exp{(-t/\tau_{\mathrm{slow}})}+C\exp{(-t/\tau_{\mathrm{cool}})}$. The stretched exponential describes the relaxation process from 5 ns to 1 $\mu$s, and the two exponentials describe the signal increase from 1-320 $\mu$s and signal decay from re-hybridization induced by thermal relaxation back to the initial temperature. The fitting parameters $A$, $B$, and $C$ correspond to the relative amplitudes of the three kinetic responses and the stretch factor $\beta$ to the heterogeneity of fraying dynamics at the fast timescale. A testable prediction of our hypothesis is that the long-lived out-of-register shifted states in AT-all should result in a significantly smaller value for the fitted $\beta$ parameter relative to those for GC-end, GC-core, and GC-mix. This hypothesis was supported by the experimental time series at both 1600 cm$^{-1}$, where $\beta_\mathrm{AT-all}$ = 0.3 compared to $\beta_\mathrm{GC-end}$ = 0.6, $\beta_\mathrm{GC-core}$ = 0.7, and $\beta_\mathrm{GC-mix}$ = 0.6, and 1660 cm$^{-1}$, where $\beta_\mathrm{AT-all}$ = 0.4 compared to $\beta_\mathrm{GC-end}$ = 0.7, $\beta_\mathrm{GC-core}$ = 0.6, and $\beta_\mathrm{GC-mix}$ = 0.6. This result supports our hypothesis and validates a testable dynamical prediction of our sequence-dependent MSMs.

@@

\section*{Supporting Information Available}

The following files are available free of charge.

\begin{itemize}
\item SI.pdf
\end{itemize}

\section*{Conflict of Interest Statement}

A.L.F.\ is a co-founder and consultant of Evozyne, Inc.\ and a co-author of US Provisional Patents 62/853,919 and 62/900,420 and International Patent Applications PCT/US2020/035206 and PCT/US20/50466.

\section*{Acknowledgements}

This material is based upon work supported by the National Science Foundation under Grant No.\ CHE-1841805. This work was completed in part with resources provided by the University of Chicago Research Computing Center. We gratefully acknowledge computing time on the University of Chicago high-performance GPU-based cyberinfrastructure supported by the National Science Foundation under Grant No. DMR-1828629.
